---
title: "Get started"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Get started}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "figures/",
  out.width = "100%"
)
```

```{r setup, message=FALSE}
library(provolleyballr)
library(dplyr)
library(tidyr)
```

# Introduction

The `{provolleyballr}` R package provides functions for extracting statistics from [League One Volleyball (LOVB)](https://lovb.com) and [Pro Volleyball Federation (PVF)](https://provolleyball.com) websites. This vignette demonstrates how use the functions and included team and player data.

## Available Data

The package includes four main datasets created with the `group_stats()` function: player season and team match data for LOVB and PVF.

```{r data-overview}
# Load LOVB individual player data  
head(lovb_player_data)

# Load LOVB team match data
head(lovb_team_data)

# Load PVF individual player data  
head(pvf_player_data)

# Load PVF team match data
head(pvf_team_data)
```



# Conclusion

This vignette demonstrates various approaches to analyzing PVF data using the **provolleyballr** package. The included datasets provide rich opportunities for:

- Team performance evaluation
- Individual player assessment  
- Role-based analysis
- Statistical modeling and prediction
- Comparative studies across teams and seasons

For more advanced analyses, consider combining this data with external sources or developing custom metrics specific to volleyball analytics.